% multiple1902 <multiple1902@gmail.com>
% doctor.tex
% Copyright 2011~2012, multiple1902 (Weisi Dai)
% https://code.google.com/p/xjtuthesis/
% 
% It is strongly recommended that you read documentations located at
%   http://code.google.com/p/xjtuthesis/wiki/Landing?tm=6
% in advance of your compilation if you have not read them before.
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
% The latest version of this license is in
%   http://www.latex-project.org/lppl.txt
% and version 1.3 or later is part of all distributions of LaTeX
% version 2005/12/01 or later.
%
% This work has the LPPL maintenance status `maintained'.
% 
% The Current Maintainer of this work is Weisi Dai.
%
\documentclass[
    doctor,
    truefont,
    %nofont, % remember to manally set the fonts
    pdflinks,
    %colorlinks,
    %compact,
    ]{xjtuthesis}

\usepackage[vlined,ruled,linesnumbered]{algorithm2e}    
\usepackage{booktabs}
\renewcommand{\eqref}[1]{公式（\ref{#1}）}
\newcommand{\figref}[1]{图~\ref{#1}~}
\renewcommand{\algorithmcfname}{\bf ~算法~ }


\ifnum 3>4
%明审
\def\authornames{\BlindPeerReviewOFF}
\def\swithON{\BlindPeerReviewOFF}
\else
%盲审
\def\authornames{\BlindPeerReview}
\def\swithON{\BlindPeerReviewON}
\fi
\graphicspath{{figures/}}

\begin{document}

\input{../body/meta.tex}

\xjtuchead
\xjtuehead
\xjtucinfopage
\xjtueinfopage
\xjtutoc
\xjtutoe
\clearpage

\input{../body/denotation_utf8.tex}

\xjtucontent

\parskip 0.5mm plus 1pt

\input{../body/preface_utf8.tex}

%\input{../body/handover_utf8.tex}
%
\input{../body/cacop_utf8.tex}
%
\input{../body/nash_bargaining_utf8.tex}
%
\input{../body/bayesian_utf8.tex}
%
\input{../body/handover_utf8.tex}
%
\input{../body/conclusions_utf8.tex}

\xjtuendcontent
\bibliographystyle{GBT7714-2005NLang-UTF8}
\xjtubib{../reference/Mendeley_Collection}

%\xjtuappendix
	\xjtuspchapter{附录}{附录 \quad 视频特征拟合结果}{Appendix }
    \input{../body/appendix.tex}

%\xjtuendappendix

\xjtuspchapter{致谢}{致\qquad 谢}{Acknowledgements}

\ifx\authornames\swithON
    \input{../body/ack_utf8.tex}
%明审
\else
%盲审
\fi

    

\xjtuspchapter{攻读博士期间取得的研究成果}{攻读博士期间取得的研究成果}{Achievements}
\begin{spacing}{1.2}
\ifx\authornames\swithON
{\wuhao \leftskip=3ex\parindent=-3ex
%      \begin{enumerate}[{[}1{]}]
[1] Yan  ZW , Liu GZ , Su R. Call Admission Control Scheme with Normalized Quality of Service Metric in IEEE802.16 Networks[J].  Wireless Communication and Mobile Computing. Accepted. (SCI 源, DOI: 10.1002/wcm.2343).

[2] Yan ZW. Optimal Call Admission Control Solution with Normalized Multimedia QoS[J]. Asian Transactions on Fundamentals of Electronics, Communication \& Multimedia, 2012, 2(2): 1-7.

%\item Yan  ZW , Liu GZ , Su R. Call Admission Control Scheme with Multimedia 
%Scheduling Service in WiMAX Network[J].  Advances in Multimedia International Journal, 2012, 3(1). 

[3] Yan ZW ,  Huang L, Kuo CCJ .   Seamless high-velocity handover support in mobile WiMAX networks[C] //  The 11th IEEE  International Conference on Communication Systems (ICCS).  IEEE Computer Society, 2008:1680 -1684 (EI:20091411996161)

%:20091411996161
[4] Yan  ZW , Liu GZ , Su R, etal  A simulation
mechanism for video delivery researches[C]// Fourth International Conference on Communications and Networking in China. Xian, China: IEEE Press, 2009: 300-304 (EI:20095112557688)

%:20095112557688
[5] 刘贵忠, 苏睿, 燕志伟, 陈晓闽, 张庆, 陈立水.  面向 H.264/AVC 视频编解码器的实时视频网络传输仿真系统[C] //第二届和谐人机环境联合学术会议(HHME06)-第15届中国多媒体学术会议（NCMT06）会议论文集, 清华大学出版社, 2006: 145 - 151.
%\end{enumerate}
%明审

[6]  苏睿,戈晓旦,燕志伟,王玥.基于Power架构的视频压缩IP核验证平台.IBM大中华区Power架构应用设计大赛 冠军. IBM,2006-12.


%要空一行

}
\else
%盲审v
{\wuhao \leftskip=3ex\parindent=-3ex
%      \begin{enumerate}[{[}1{]}]
[1] Call Admission Control Scheme with Normalized Quality of Service Metric in IEEE802.16 Networks[J].  Wireless Communication and Mobile Computing. (DOI: 10.1002/wcm.2343).

[2] Optimal Call Admission Control Solution with Normalized Multimedia QoS[J]. Asian Transactions on Fundamentals of Electronics, Communication \& Multimedia, 2012, 2(2): 1-7.

%\item Yan  ZW , Liu GZ , Su R. Call Admission Control Scheme with Multimedia 
%Scheduling Service in WiMAX Network[J].  Advances in Multimedia International Journal, 2012, 3(1). 

[3] Seamless high-velocity handover support in mobile WiMAX networks[C] //  The 11th IEEE  International Conference on Communication Systems (ICCS).  IEEE Computer Society, 2008:1680 -1684 (EI: 20091411996161)

%:20091411996161
[4] A simulation mechanism for video delivery researches[C]// Fourth International Conference on Communications and Networking in China. Xian, China: IEEE Press, 2009: 300-304 (EI: 20095112557688)

%:20095112557688
[5] 面向 H.264/AVC 视频编解码器的实时视频网络传输仿真系统[C] //第二届和谐人机环境联合学术会议(HHME06)-第15届中国多媒体学术会议（NCMT06）会议论文集, 清华大学出版社, 2006: 145-151.

[6] 基于Power架构的视频压缩IP核验证平台.IBM大中华区Power架构应用设计大赛 冠军. IBM,2006-12.

%要空一行

}
%\end{enumerate}
\fi
\end{spacing}

\xjtuacademicintegrity


\end{document}

